GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-16 ennv.tex

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figure/dnn.pdf}
    \caption{\label{fig:dnn} An FNN with ReLU.}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[width=0.5\linewidth]{figure/dnn.pdf}
%     \caption{\label{fig:dnn} An FNN with ReLU.}
% \end{figure}

\section{Types of Neural Networks}

\paragraph{Feed-Forward Network (FFN)} In an FFN information flows in one direction, from the input layer to hidden layers to the output layer (and thus no cycle).

A fully connected feed-forward neural network (FNN), shown below, is an FFN where every neuron in a layer is connected to every neuron in the next layer.
\begin{center}
\begin{tikzpicture}[scale=0.8, transform shape]
% Input Layer
\node at (0,4) {\textbf{Input Layer}};
\foreach \x in {1,2,3,4} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (I\x) at (0,4-\x) {};
}

% Hidden Layer 1
\node at (3,4) {\textbf{Hidden Layer 1}};
\foreach \x in {1,2,3,4,5} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (H1\x) at (3,4.5-\x) {};
}

% Hidden Layer 2
\node at (6,4) {\textbf{Hidden Layer 2}};
\foreach \x in {1,2,3,4,5} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (H2\x) at (6,4.5-\x) {};
}

% Output Layer
\node at (9,3.5) {\textbf{Output Layer}};
\foreach \x in {1,2,3} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (O\x) at (9,3.5-\x) {};
}

% Connections
\foreach \i in {1,2,3,4}
    \foreach \j in {1,2,3,4,5}
        \draw[->] (I\i) -- (H1\j);

\foreach \i in {1,2,3,4,5}
    \foreach \j in {1,2,3,4,5}
        \draw[->] (H1\i) -- (H2\j);

\foreach \i in {1,2,3,4,5}
    \foreach \j in {1,2,3}
        \draw[->] (H2\i) -- (O\j);

\end{tikzpicture}
\end{center}

\paragraph{Convolutional Neural Networks (CNNs)} are a type of neural network that is often used in image recognition and classification.  CNNs consist of of neurons that have learnable weights and biases. Each neuron receives several inputs, takes a weighted sum over them, passes it through an activation function, and responds with an output.

\paragraph{Recurrent Neural Networks} Recurrent Neural Networks (RNNs) are a type of neural network that is often used in natural language processing and speech recognition. RNNs are designed to recognize patterns in sequences of data. RNNs have loops in them, allowing information to persist. This loop allows information to be passed from one step of the network to the next.

\paragraph{Residual Networks} Residual Networks (ResNets) are a type of neural network that is often used in image recognition and classification. ResNets introduce skip connections that allow the gradient to flow directly through the network, making it easier to train deep networks.
